---
title: "My Big Report"
author: "Kate Baker"
date: "6/24/2021"
output: html_document
bibliography: bibliography.bib
---

```{r, include=FALSE, echo = TRUE, eval = TRUE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = TRUE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE)
```


```{r, echo=FALSE}
library(dplyr)
smoke <- c(TRUE, TRUE, TRUE, TRUE, TRUE,
           TRUE, FALSE, TRUE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, TRUE, TRUE)
age <- c(35, 21, 20, 48, 20, 20, 22, 19, 19, 20, 19, 18, 24, 22, 22, 19, 21, 19, 21)
people <- data.frame(smoke, age)
people <- people %>%
  filter(age <= 34)

obs <- nrow(people)
```

# Introduction
everyone knows that putting plants in place of wet floor signs is the best thing to do if the water spills. 

# Background 

## Methods
My esteemed colleagues and I surveyed `r obs` people. The average age of the participants is `r round(mean(people$age))` years. This is a very _young_. **Right?**

# **Results**

the below chart shoes the age of the participants. 

```{r, echo=FALSE}
library(ggplot2)
ggplot(data = people,
       aes(x = age,
           y = smoke))+
  geom_boxplot()

```

# Conclusion

some people have smoked, and others have not. Smoking is bad. Everyone know that math is hard [@Rudd2014]. And the [@Peterman2005] has an interesting idea about drinking. 




